\newglossaryentry{GPU}{%
    name={GPU},%
    description={Graphics Processing Unit, an acronym for graphic card.}}
    
\newglossaryentry{CPU}{%
    name={CPU},%
    description={Central Processing Unit, also known as processor.}}

\newglossaryentry{DGX}{%
    name=DGX Station,%
    description={A powerful Nvidia GPU configuration}}

\newglossaryentry{Engie}{%
    name=Engie,%
    description={French-based energy company where the intership was held}}

\newglossaryentry{NLP}{%
    name=NLP,%
    description={Natural Language Processing}}
   
\newglossaryentry{Engie Crigen}{%
    name=Engie Crigen,%
    description={The research laboratory of Engie}}
    
\newglossaryentry{CSAI}{%
    name=CSAI,%
    description={Computer Science And Artificial Intellience Lab, a sub lab of Engie Crigen. It is the team where I worked at Engie}}
    
\newglossaryentry{re-id}{%
    name=re-id,%
    description={Object re-identification, it aims at recognizing the same object across different cameras}}
    
\newglossaryentry{ECCV}{%
    name=ECCV,%
    description={European Conference of Computer Vision, the conference I attended in Munich}}
    
\newglossaryentry{CNN}{%
    name=CNN,%
    description={Convolutional Neural Network, the most used model in Computer Vision}}
    
\newglossaryentry{ResNet-50}{%
    name=ResNet-50,%
    description={A CNN-based model learning residual mapping function. This model is a impressive trade-off between time complexity and accuracy}}
    
\newglossaryentry{DML}{%
    name=DML,%
    description={Deep Metric Learning aims at learning an embedding function modeled as deep neural network.}}

\newglossaryentry{feature extractor}{%
    name=feature extractor,%
    description={A model that takes an input image and output a feature vector, also called embedding}}
    
\newglossaryentry{embedding}{%
    name=embedding,%
    description={An embedding in re-id task, is a feature vector produced by a feature extractor model}}
    
\newglossaryentry{deep learning}{%
    name=deep learning,%
    description={A machine learning field using models composed of a large number of artificial neurons. Deep learning is explained in Section~\ref{deeplearning}.}}
    
\newglossaryentry{MLP}{%
    name=MLP,%
    description={Multi-Layer Perceptron is non linear model composed of fully connected layers of artificial neurons.}}
    
\newglossaryentry{mapping function}{%
    name=mapping function,%
    description={In the context of deep learning, a mapping function is usually modeled as a neural network. More precisely, the model maps an input into a different output space}}
    
\newglossaryentry{objective function}{%
    name=objective function,%
    description={In the context of deep learning, a objective function is the training loss}}
    
\newglossaryentry{FC}{%
    name=FC,%
    description={A layer is said Fully Connected when all its neurons are linked to each others}}


